ABC inferences

### 2024-12-16 extensive_tests/abc_inferences/draft-abc-inferences-vignette.Rmd
Adding script to get spatial structure

```{r}
# Load data
file_path <- "CGI-Mzebra.txt" # Adjust the path if necessary
cgi_data <- read.table(file_path, header = TRUE, sep = "\t")

@@

@@

```{r}
head(cgi_data[cgi_data$chr == "NC_036801.1",])
```

## How to generate the structural distribution .RData file from the reference genome and the CGI annotation

@@

```{r}
load("genomic_dist/CpG_count.RData")

```
29502362..29517382

```{r}
# Filter the data for the given chromosome and region
dpp4_chr <- "NC_036801.1"
filtered_data <- CpG_count[CpG_count$chr == dpp4_chr & CpG_count$start > 2.8e7 & CpG_count$end < 3e7, ]

@@

  if (filtered_data$str[i] == 0) {
    # Non-island (blue)
    rect(filtered_data$start[i], 0, filtered_data$end[i], 
         filtered_data$CpG_count[i], col = "blue", border = "blue")
  } else {
    # Island (red)
    rect(filtered_data$start[i], 0, filtered_data$end[i], 
         filtered_data$CpG_count[i], col = "red", border = "red")
  }
}

@@

# Filter the data for the given chromosome and region
dpp4_chr <- "NC_036801.1"
dpp4_start <- 29502362
dpp4_end <- 29517382
filtered_data <- CpG_count[CpG_count$chr == dpp4_chr & CpG_count$start > dpp4_start - 5e5 & CpG_count$end < dpp4_end + 5e5, ]

>>>>

```{r}
# Load data
file_path <- "genomic_dist/CGI-Mzebra.txt" # Adjust the path if necessary
cgi_data <- read.table(file_path, header = TRUE, sep = "\t")

@@

## Fixed DMR found in paper: Associated genes

Add reference

@@

Lets explore *Dpp4*, as it is associated with differential gene expression and it is located in a better characterized genomic region:

```{r}
dpp4_chr <- "NC_036801.1"
dpp4_start <- 29502362
dpp4_end <- 29517382
```

## Explore the CpG counts in islands and non islands generated from the reference genome and the CGI annotation

@@

```{r}
load("genomic_dist/CpG_count.RData")
```

```{r}
# Filter the data for the given chromosome and region
filtered_data <- CpG_count[CpG_count$chr == dpp4_chr & CpG_count$start > dpp4_start - 5e5 & CpG_count$start < dpp4_end + 5e5, ]

@@

  if (filtered_data$str[i] == "Non-island") {
    # Non-island (blue)
    rect(filtered_data$start[i], 0, filtered_data$end[i], 
         filtered_data$CpG_count[i], col = "blue", border = "blue")
  } else {
    # Island (red)
    rect(filtered_data$start[i], 0, filtered_data$end[i], 
         filtered_data$CpG_count[i], col = "red", border = "red")
  }
}

@@

# Filter the data for the given chromosome and region
filtered_data <- CpG_count[CpG_count$chr == dpp4_chr & CpG_count$start > dpp4_start - 5e5 & CpG_count$end < dpp4_end + 5e5, ]
